Summary Tables

### 2020-01-09 summary_tables.Rmd
Distance prop by categories

>>>>

## Distance by distance category
### Tables

```{r trip_dist_mode_figs = "asis"}

for (city in cities){

  df <- io[[city]]$trip_scen_sets %>% filter(scenario == 'Baseline') %>% distinct(trip_id, .keep_all = T) %>% group_by(trip_distance_cat) %>% summarise(sum_dist = sum(trip_distance), n_vals = n(), prop = round(n_vals / nrow(.) * 100, 1))
  print(kable(df, caption = paste("Distance by mode by for  ", city)))
}

<!-- ### Figures -->

<!-- ```{r trip_dist_mode_figs = "asis"} -->

<!-- for (city in cities){ -->

<!--   df <- io[[city]]$trip_scen_sets %>% filter(scenario == 'Baseline' & trip_mode %in% c('walking', 'bicycle', 'car', 'motorcycle', 'bus')) %>% distinct(trip_id, .keep_all = T) %>% group_by(trip_mode, trip_distance_cat) %>% summarise(sum_dist = sum(trip_distance), n_vals = n()) %>%  -->
<!--     group_by(trip_mode) %>% mutate(n_vals_1 = sum(n_vals)) %>%  -->
<!--     mutate(prop = round(n_vals/n_vals_1 * 100, 1)) -->

<!--   print(ggplot(data=df, aes(x=trip_distance_cat, y=prop)) + -->
<!--           geom_bar(stat="identity", fill="steelblue")+ -->
<!--           facet_wrap(vars(trip_mode)) + -->
<!--           geom_text(aes(label=prop), vjust = -0.3, size = 3.5)+ -->
<!--           theme_minimal() + -->
<!--           theme(panel.spacing = unit(2, "lines")) + -->
<!--           labs(title = paste(city, ' by dist by mode'))) -->
<!-- } -->

<!-- ``` -->
